Global case

### 2025-07-25 AAAI2026/Lipitschz.tex
correct the version
add tables

@@

	\subsection{Comparison of different modelings}

	\subsection{Comparison of different scoring algorithms}

>>>>

	\input{introduction}

@@

	\subsection{Experiment results for Pipe system}

	For the pipe system, to find a example of large difference on outputs is one of the main aims.

	The network of Pipe system is relatively simple and in the tests, we will open all $\ReLU$ nodes.

	We will compare the results of different modeling methods.

\begin{tabular}{|l|l|l|l|l|}\hline
L1 Diff <= 0.82378 &        Bound &  Solution &                          Real &  Time \\\hline
	1v,open 100 &     0.035613 &  0.035613 &                       0.01288 & 10608 \\\hline
	3v,open 100 &     0.040074 &  0.028934 &                      0.021441 & 10922 \\\hline
	3v,open 100 &     0.039824 &  0.028832 &                      0.022255 & 22153 \\\hline
	2v,open 100 &     0.046719 &  0.024364 &                      0.024436 & 10922 \\\hline
\end{tabular}

	And

	\begin{tabular}{|l|l|l|l|l|}\hline
	 L1 Diff <= 0.82378 &        Bound &  Solution &                          Real &  Time \\\hline
		1v,open 100 &     0.035613 &  0.035613 &                      0.019141 &   984 \\\hline
		3v,open 100 &     0.041382 &  0.025433 &                      0.016638 &  1082 \\\hline
		3v,open 100 &      0.03496 &  0.027206 &                      0.021607 & 14523 \\\hline
		3v,open 100 &     0.032906 &  0.027655 &                      0.016481 & 72126 \\\hline
		2v,open 100 &     0.041787 &  0.022805 &                      0.022882 &  1082 \\\hline
		2v,open 100 &     0.035964 &  0.023563 &                      0.023608 & 14523 \\\hline
	\end{tabular}

	\subsection{Experiment results for MNIST}

	\begin{tabular}{|l|l|l|l|l|l|}\hline
		& Method & Bound & Solution & Real & Time \\\hline
		54 & 2v,open 75x5 & 21.013510 & 8.467282 & 0.222900 & 43200 \\\hline
		55 & 2v,open 90x5 & 12.009719 & 3.440846 & 0.258480 & 43200 \\\hline
		56 & 2v,open 97x5 & 20.646000 & 1.915210 & 0.372200 & 129626 \\\hline
		57 & 2v,open 100x5 & 8.760835 & nan & nan & 43200 \\\hline
		58 & 2v,open 100x5 & 8.257397 & nan & nan & 259200 \\\hline
		59 & 1v,open 75x5 & 17.472430 & 0.908984 & 0.091740 & 43200 \\\hline
	\end{tabular}
